\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{amssymb}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\Large Brendan McCann} & Email : \href{mailto:brendan.mccann02@gmail.com}{brendan.mccann02@gmail.com}\\
		Dublin, Ireland & Mobile : +353 85 111 4619 \\
		\href{https://www.linkedin.com/in/brendan-mccann-6b3300268/}{LinkedIn} & \href{https://github.com/brendanmcc02}{GitHub}
	\end{tabular*}
	
	%\section{Introduction}
	%Hi! I'm a 4th-year Computer Science Student.
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Trinity College Dublin}{Sept. 2020 -- May 2026}
	{Masters in Computer Science M.C.S}{Grade: First Class Honours}
	\begin{itemize}
		\item Awarded the Victor W. Graham Prize as a result of achieving the highest mark in the 1st year Maths Summer exam.
		\item \textbf{Languages:} Java, SQL, R, C, C++, Assembly.
	\end{itemize}
	\resumeSubHeadingListEnd
	
	
	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Microsoft}{June -- August 2024}
	{Software Engineer Intern}{Dublin, Ireland}
	\begin{itemize}
		\item Tasked with migrating a service (processes $\sim$34 billion requests/day) from .NET6 to .NET8
		\item After completion, my projected was project to save \$520,000 over the next 3 years.
		\item Experienced extensive cross-team communication, as the products I was working on were not owned by my team.
		\item Assisted in the organisation of a company-wide Counter-Strike 2 gaming tournament. Additionally, I was the MC for the event.
		\item \textbf{Technologies}: C\#, .NET Core, Service Fabric.
	\end{itemize}
	
	\resumeSubheading
	{Five Guys Burgers \& Fries}{Dec. 2021 -- Jan. 2024}
	{Team Leader}{Dublin, Ireland}
	\newline\newline 
	A Team Leader is one step underneath a manager. When the manager is not around, I was the one in charge of running the kitchen.
	\begin{itemize}
		\item Led the kitchen and delegated tasks to other crew members throughout service.
		\item First point of contact for customer issues \& complaints.
		\item Worked 20 hours/week during University.
	\end{itemize}
	
	\resumeSubHeadingListEnd
	
	%-----------PROJECTS-----------------
	\section{Projects}
	\begin{itemize}
		\item \textbf{\href{https://github.com/brendanmcc02/film-rec}{Film Recommender System:}} No deep learning libraries were used, as I wanted to know how they were built from the ground up. Solo project during my studies. \textbf{Technologies: Python.}
		\item \textbf{\href{https://github.com/hacktrinity-unreal/live-summariser}{Live Court Case Summarizer:}} Collaborated in a 4-person team for the HackTrinity Weekend Hackathon. We won the MVP Bonus Prize. \textbf{Technologies: Python Flask, React JS.}
		\item \textbf{\href{https://github.com/Sweng-Group-4/sweng-group-4}{AI-Powered Multilingual Image Search:}} Group project in University, partnering with Shutterstock. Chosen as the Team Leader of an 11-person team. Managed 3 sub-teams simultaneously, and was the main point of contact with our client in Shutterstock and the module demonstrators. Hands-on experience with the Agile methodology.
		\item \textbf{\href{https://github.com/hacktrinity-unreal/live-summariser}{Film Data Visualisation:}} A \href{https://brendanmcc02.github.io/film-data-vis/web/index.html}{Website} with several graphs of my personal film ratings. Automated a weekly shell script to web scrape data from my IMDb profile. Solo project during my studies. \textbf{Technologies: JavaScript, Node JS, Shell Script, HTML, CSS.}
	\end{itemize}
	
	%-------------------------------------------
\end{document}
